---
title: "Breast cancer survival"
output: html_notebook
---

```{r}
path <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(path)
```
```{r}
breast_cancer <- readRDS("metabric-analytical.rds")
head(breast_cancer)
```

I want to assess what the different cancer types are
```{r}
unique(breast_cancer$cancer_type)
sum(is.na(breast_cancer$cancer_type == "NA"))
```
I want to assess whether there are any cancers with 
```{r}
sum(breast_cancer$tumor_stage == 0, na.rm=TRUE)
```

# Aim 2: How does molecular signature influence survival
```{r}
breast_cancer <- breast_cancer %>%
  mutate(
    overall_status = ifelse(vital_status == "died of disease", "dead", "censored")
  ) %>%
  drop_na(overall_status)
```

# Is cellularity an important prognostic indicator for survival 
log rank test for each exposures 
```{r}
survdiff(Surv(surv_months, status) ~ grade, data = breast_cancer)
```

```{r}
survdiff(Surv(surv_months, status) ~ tumor_size, data = breast_cancer)
```

```{r}
survdiff(Surv(surv_months, status) ~ cellularity, data = breast_cancer)
```

```{r}
survdiff(Surv(surv_months, status) ~ tumor_stage, data = breast_cancer)
```


Kaplan Meier plot w/o the censored data vertical thingy
```{r}
survfit2(Surv(surv_months, status) ~ tumor_stage, data = breast_cancer) %>%
  ggsurvfit() + 
  labs(
    x = "Months",
    y = "Survival probability"
  )
```

```{r}
survfit2(Surv(surv_months, status) ~ tumor_size, data = breast_cancer) %>%
  ggsurvfit() + 
  labs(
    x = "Months",
    y = "Survival probability"
  )
```

```{r}
survfit2(Surv(surv_months, status) ~ grade, data = breast_cancer) %>%
  ggsurvfit() + 
  labs(
    x = "Months",
    y = "Survival probability"
  )
```

```{r}
survfit2(Surv(surv_months, status) ~ cellularity, data = breast_cancer) %>%
  ggsurvfit() + 
  labs(
    x = "Months",
    y = "Survival probability"
  )
```


Kaplan Meier plot with the censored data
I think need to install survminer?
```{r}
install.packages("survminer")
```

```{r}
surv_size_fit = survfit(
  survival::Surv(surv_months, status) ~ tumor_size,
  data=breast_cancer)
survminer::ggsurvplot(surv_size_fit, risk.table = TRUE)
```

```{r}
surv_stage_fit = survfit(
  survival::Surv(surv_months, status) ~ tumor_stage,
  data=breast_cancer)
survminer::ggsurvplot(surv_stage_fit, risk.table = TRUE)
```

```{r}
surv_grade_fit = survfit(
  survival::Surv(surv_months, status) ~ grade,
  data=breast_cancer)
survminer::ggsurvplot(surv_grade_fit, risk.table = TRUE)
```

```{r}
surv_cell_fit = survfit(
  survival::Surv(surv_months, status) ~ cellularity,
  data=breast_cancer)
survminer::ggsurvplot(surv_cell_fit, risk.table = TRUE)
```


